\sectionTitle{Work Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
        \experience
	{Now}   {CTO and Founder}{Lumen Labs - Talkkit, Turin, IT}
	{January 2024} {
		\begin{itemize}
			\item Founder and CTO of a startup in the Ed-Tech sector. Our product, Talkkit, is a language-learning application that enables users to converse with a virtual avatar. As the CTO and the only founder with technical expertise, I have independently developed all aspects of the product: from research and design to development and deployment in cloud environments.
		\end{itemize}
	}
	{Flutter, FastAPI, Unity, Azure}
	\emptySeparator
	\emptySeparator
	\experience
	{Now}   {Full Stack Developer}{DoInn SRL, Mondovì CN, IT}
	{April 2023} {
		\begin{itemize}
			\item Data collection, analysis, design, development, testing, and deployment of web-based software solutions created on-demand for clients, including Banco Azzaglio SpA. Participated in all stages of the development lifecycle, both as a sole developer and as part of a team.
            
            Worked on 4 projects: 
            \begin{enumerate}
            \item A Sound Therapy platform with an integrated e-commerce and a custom CMS. Stack: React, Laravel, and FastAPI. 
            
            \item A chatbot with Retrieval-Augmented Generation (RAG). Stack: ExtJS, FastAPI, and QDrant. 
            
            \item A platform for managing securitizations in the financial sector. Stack: ExtJS and Laravel. 
            
            \item A platform for managing hardware rental operations. Stack: React and Laravel.
            \end{enumerate}
		\end{itemize}
	}
	{ExtJS, Laravel, React, FastAPI, QDrant}
	\emptySeparator
	\emptySeparator
	\experience
	{March 2023}   {Backend Developer}{Intervieweb SRL, Turin, IT}
	{February 2023} {
		\begin{itemize}
			\item Designed and developed features for InRecruiting using a microservices architecture.
		\end{itemize}
	}
	{Docker, Microservices, NodeJS}
	\emptySeparator
	\emptySeparator
	\experience
	{January 2023}   {Thesis Project - Data Scientist}{Alten Italia S.p.A., Turin, IT}
	{September 2022} {
		\begin{itemize}
			\item Study and analysis of Time Series data for Anomaly Detection.
			\item Application of Machine Learning methods.
		\end{itemize}
	}
	{Machine Learning, Deep Learning, Anomaly Detection, Time Series}
	\emptySeparator
	\emptySeparator
	\experience
	{September 2022}   {Full Stack Developer}{Sguang Informatica SRL, San Rocco CN, IT}
	{December 2019} {
		\begin{itemize}
			\item Web development of management software with functionalities and specifications provided by client companies using \textbf{Javascript} (Vue.js) for the front end and \textbf{Python} (Django) for the back end. Involved in all stages of design and development: from data collection to deployment on servers. 
            
            These management systems generally revolved around customer management, appointments, sales orders, quotes, rentals, interventions, or maintenance.
			\item Web hosting, domain, and VPS management using services like Aruba, Register, and Netsons.
			\item Web development of small applications with PHP.
			\item Website development using Wordpress.                         
		\end{itemize}
	}
	{Vue, Django, Wordpress, XAMPP}
	\emptySeparator
	\emptySeparator
	\experience
	{August 2018} {Junior Developer}{EOS Solutions S.p.A., Sant'Albano Stura CN, IT}
	{February 2018}    {
		Software development for the ERP Microsoft Dynamics® NAV:
		\begin{itemize}
			\item Designed and developed software for interfacing with milk analysis machines, using Microsoft Dynamics NAV.                     
		\end{itemize}
	}
	{Microsoft Dynamics NAV, Microsoft SQL Server}
	\emptySeparator
	\emptySeparator
	\experience
	{September 2017}     {Developer}{Web\&Tech Solutions, Cuneo CN, IT}
	{August 2016}    {
		\begin{itemize}
			\item Web development of management software with functionalities and specifications provided by clients using the PHP language.
		\end{itemize}
	}
	{PHP, XAMPP}
	\emptySeparator
	 
	
\end{experiences}
