\sectionTitle{Personal Project}{\faLaptop}

\begin{projects}
\project
{Talkkit}{2024}
	{Talkkit is a language learning application that allows you to converse with a virtual avatar. The mission is to offer an accessible, engaging and functional tool to become more fluent in foreign languages.
		 
		\href{https://talkkit.io/}{talkkit.io} }
	{AI,LLM,ChatBot,Apprendimento,Lingue,Mobile}
    
	\project
	{Unsupervised Anomaly Detection for a Manifacturing Industry}{2023}
	{Matser's Degree Thesis Reaserch. The research was about Unsupervised Anomaly Detection on Time Series data from a manifacturing industry.
		 
		\github{lorisgir/TESI-MAGISTRALE}. }
	{Machine Learning, Deep Learning, Time Series, Model Selection, Anomaly Detection}
	
	\project
	{Booksriver}{2022}
	{Booksriver is a mobile application. It provides a large library of books in which the user can browse, indicate their progress in reading, write reviews and follow other users. The application has been developed in three variants: Native Android using Java and XML, Native Android using Kotlin and Compose, multi-platform using Flutter.
		 
		The backend was designed through a microservices architecture in Spring: two microservices along with EUREKA, a Gateway Service and RabbitMQ. For the deployment it has been used Docker-Compose and GitLab CI. 
		 
		\github{lorisgir/Booksriver}. }
	{Spring, Java, Kotlin, Dart, Flutter, Compose, Docker, Microservizi}
	
	 
	\project
	{Design and development of a software for the management of the Individualized Care Plan}{2020}
	{Degree Thesis project. The software developed offers digital support to health care workers in the nursing homes by computerizing the compilation of the documents of the Individualized Care Plan.}
	{Vue, Django, PostgreSQL}
					
		
	
	
	
	 
	
\end{projects}