\sectionTitle{Work Experience}{\faSuitcase}
\begin{experiences}

\experience
{June 2025}   {CTO and Co-Founder}{Lumen Labs - Talkkit, Turin IT}
{January 2024} {
	\begin{itemize}
	\item Co-founder and CTO of an innovative startup in the Ed-Tech sector. Our product, \textbf{Talkkit}, is a language learning app that enables natural conversations with an \textbf{intelligent virtual avatar}. The app was developed using \textbf{Flutter} and distributed on both \textbf{iOS and Android}, integrating a \textbf{Unity} module to handle the 3D avatar, including animated models and lip-syncing.

	As CTO, I was responsible for all phases of the product life cycle: from ideation and initial research to design, development, testing, and deployment in \textbf{Azure cloud} environments. The backend was built using \textbf{FastAPI (Python)}.

	As Co-Founder, beyond technical responsibilities, I was also involved in cross-functional startup operations, covering areas like marketing, communication with potential investors, and defining the business development strategy.
	\end{itemize}
}
{Flutter, FastAPI, Unity, Azure}

\emptySeparator
\emptySeparator

\experience
{Present}   {Full Stack Developer}{DoInn SRL, Mondovì IT}
{April 2023} {
	\begin{itemize}
	\item Involved in all stages of the software development lifecycle for custom web-based solutions for clients such as \textbf{Banco Azzaglio SpA}. I handle requirements gathering, analysis, design, development, testing, and deployment—both independently and as a \textit{Team Leader}.

	Contributed to several key projects:

	\begin{enumerate}
	\item \textbf{Corporate Welfare Platform}, developed as an ecosystem composed of \textbf{four distinct interfaces} for various stakeholders: \textit{Employees}, \textit{Companies}, \textit{Merchants}, and \textit{Admins}. The system includes:
	\begin{itemize}
		\item A \textbf{Next.js} interface for the \textit{Admin panel}, managing approvals, monitoring, census, public grants, and reporting.
		\item A \textbf{Next.js} interface for \textit{Companies}, allowing onboarding of employees, welfare fund management, and expense tracking.
		\item A \textbf{React Native} app for \textit{Employees} to view available credit, request and use vouchers, and browse grants and benefits.
		\item A \textbf{React Native} app for \textit{Merchants} to manage voucher redemption and view transaction history.
	\end{itemize}
	The system is powered by a centralized \textbf{Laravel} backend exposing REST APIs and managing authentication, authorization, business logic, and integration with external services for voucher issuance and public grants.

	\item \textbf{Sound Therapy Platform}, developed to support personalized therapeutic programs, enabling healthcare professionals to assess well-being using an electromagnetic device. The platform is \textbf{multi-tenant} and features:
	\begin{itemize}
		\item \textit{End Users} with access to an e-commerce portal for purchasing products and services.
		\item \textit{Doctors} managing patients and conducting assessment programs.
		\item \textit{Admins} with a custom CMS for creating evaluation programs and managing configurations.
	\end{itemize}
	\textit{Stack: React, Laravel, FastAPI}.

	\item \textbf{RAG Chatbot} (Retrieval-Augmented Generation), integrated with an internal document archive in a banking intranet. It allows retrieval and contextual consultation of PDF content using GPT models and a vector engine powered by \textbf{QDrant}. \textit{Stack: Sencha Ext JS, FastAPI, QDrant}.

	\item \textbf{Securitization Management System} for internal use within a banking institution. It enables the complete management of securitization operations with focus on \textbf{data versioning}, \textbf{data validation}, and \textbf{official report generation} for communication with other financial institutions and authorities. \textit{Stack: Sencha Ext JS, Laravel}.

	\item \textbf{Hardware Rental Platform}, a \textbf{multi-tenant} system for companies renting tech equipment. Each company has its own dashboard to manage clients, configure products, set prices, and generate rental orders. \textit{Stack: React, Laravel}.
	\end{enumerate}
	\end{itemize}
}
{NextJS, Sencha Ext JS, Laravel, React, FastAPI, QDrant}

\emptySeparator
\emptySeparator

\experience
{January 2023}   {Thesis Internship - Data Scientist}{Alten Italia S.p.A., Turin IT}
{September 2022} {
	\begin{itemize}
		\item Studied and analyzed time series data for anomaly detection.
		\item Applied machine learning methods for detecting irregular patterns.
	\end{itemize}
}
{Machine Learning, Deep Learning, Anomaly Detection, Time Series}

\emptySeparator
\emptySeparator

\experience
{September 2022}   {Full Stack Developer}{Sguang Informatica SRL, San Rocco IT}
{December 2019} {
	\begin{itemize}
		\item Developed web-based management software according to client specifications using \textbf{JavaScript} (Vue.js) for frontend and \textbf{Python} (Django) for backend. Involved in all phases of the process—from data gathering to server deployment.

		These systems typically focused on customer management, appointments, sales orders, quotes, rentals, interventions, or maintenance operations.
		
		\item Managed web hosting, domains, and VPS through services such as Aruba, Register, and Netsons.
		\item Developed small web applications in PHP.
		\item Built websites using WordPress.
	\end{itemize}
}
{Vue, Django, WordPress, XAMPP}

\end{experiences}
